Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-06-04 performance_comparison.tex
[mg] subsec 5.3 ol VS cl

%---Axle saturation
After analyzing the variations of these four key signals with respect to the nominal solution, we now turn our attention to the evaluation of axle saturation, which provides insight into how close each configuration operates to the tire grip limits. 
In accordance with the FLC formulation introduced in~\ref{eq:adherence_constraint}, we define the \emph{axle saturation ratio} $S_j$ as
\begin{equation}
	S_j = \frac{ \left( \frac{X_j(\bx,\bu)}{\mu_{x,j}} \right)^2+ \left( \frac{Y_j(\bx,\bu)}{\mu_{y,j}}\right)^2}{Z_j^2(\bx,\bu)}.
\end{equation}
This quantity indicates how close each configuration operates to the friction limit; $S_j = 1$ when the point $\left(X_j, Y_j\right)$ lies exactly on the friction ellipse, i.e., under full saturation.
Figure~\ref{fig:ol_saturation} shows the values of $S_j$ for the front axle ($j=1$, first panel) and the rear axle ($j=2$, rear panel) for the previously introduced configurations: the nominal case (black dashed line) and the three robustified cases (color-coded as before).

@@

\subsection{Comparison between open-loop and closed-loop approaches}

>>>>

%---Axle saturation
After analyzing the variations of these four key signals with respect to the nominal solution, we now turn our attention to the evaluation of axle saturation, which provides insight into how close each configuration operates to the tire grip limits. 
In accordance with the FLC formulation introduced in~\eqref{eq:adherence_constraint}, we define the \emph{axle saturation ratio} $S_j$ as
\begin{equation}
	S_j = \frac{ \left( \frac{X_j(\bx,\bu)}{\mu_{x,j}} \right)^2+ \left( \frac{Y_j(\bx,\bu)}{\mu_{y,j}}\right)^2}{Z_j^2(\bx,\bu)}.
\end{equation}
This quantity indicates how close each configuration operates to the friction limit; $S_j = 1$ when the point $\left(X_j, Y_j\right)$ lies exactly on the friction ellipse, i.e., under full saturation.
Figure~\ref{fig:ol_saturation} shows the values of $S_j$ for the front axle ($j=1$, first panel) and the rear axle ($j=2$, rear panel) for the previously introduced configurations: the nominal case (black dashed line) and the three robustified cases (color-coded as before).

@@

\subsection{Open-loop vs Closed-loop evaluation}
We now compare the open-loop planning with the closed-loop approach. In particular, we consider open-loop and closed-loop trajectories computed using both the robustified TLC and FLC, with $\ga^\textrm{TLC}=\ga^\textrm{FLC}=1.28$. As before, the open-loop planning is carried out with a prediction horizon of $H=4$ steps.

For the TLC, the back-off term $\be^{TLC}$ in~\eqref{eq:TLC} admits a clear geometrical interpretation: it corresponds to the amount by which the track boundaries are tightened to meet the probabilistic constraint, or, equivalently, to a virtual extension of the vehicle's width. According to the latter interpretation, Figure~\ref{fig:olcl_traj_bands} shows two highlighted bands---red for the open-loop case and cyan for the closed-loop case---corresponding to the area swept by the back-off-extended-vehicle. Ultimately, the TLC enforces precisely that these bands remain entirely within the actual track limits. The comparison between the two regions illustrates how the additional conservativeness of the open-loop approach stems from larger back-off terms, i.e., a wider band that must stay within the track boundaries. The closed-loop method, on the other hand, benefits from the LQR-based feedback, which allows it to maintain smaller back-off terms and thus a narrower band, requiring a reduced safety margin from the track limits.

\begin{figure}
	\centering
	\includegraphics{Fig/olcl_traj_bands.pdf}
	\caption{Lorem ipsum.}
	\label{fig:olcl_traj_bands}
\end{figure}
